### 2016-04-24 ch03-lrm/lrm-paper.tex
Many TODOs in ch03

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
\end{equation}

\begin{figure}
 \centering
  \input{\thisDir/figs/generalized-output-error.tikz}
  \caption{Block schematic used in the simulations}
\end{figure}

\TODO{H0}

The \gls{SNR} in the system bandwidth $\BW$ is defined as
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
            {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\BW$ is the $3 \unit{dB}$ bandwidth of the system.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[Example spectra]
  \label{fig:nparam:spectra}
\end{figure}

We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over all  Monte Carlo runs.
Specifically, the following values
\begin{align}
  \sampleMean{\bullet}(\omega_k) & 
  \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k)
  \\
  \sampleBias{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
    = 
    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
    \\
    \sampleVariance{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC - 1}
    \sum_{i=1}^{\nMC}
                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
\end{align}
are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$.

  % \subsection{Implications of the model structure}
  \subsection{Implications of the noise level}
  % \subsection{Implications of the noise coloring}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
\end{figure}

\TODO{describe aggregation over $\omega$}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

@@

\begin{remark}
In all the simulations, it can be seen that for $\nWind \to \infty$, the error tapers off.
\TODO{andere pieken gaan in de praktijk alles om zeep helpen en dus bovengrens stellen}
\end{remark}

>>>>

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
                                      \text{,}
\end{equation}
this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$.
The system is scaled such that its peak amplitude is $3\unit{dB}$ and the 
As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
The gain of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
            {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to $\set{10, 20, 40, 60, \infty} \unit{dB}$.

\begin{figure}
 \centering
  \input{\thisDir/figs/generalized-output-error.tikz}
  \caption{Block schematic used in the simulations. }
  \label{fig:nparam:blockH0}
\end{figure}

The input signal used is a random-phase multisine with a full linear grid.
A number of samples of the input- and output are measured, in such a way that the \gls{DFT} grid excited $\nBW$ bins within the $3\unit{dB}$ bandwidth of the system.
The different values for $\nBW \in \set{2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 14, 16, 32, 40, 64, 80, 92, 128, 256}$ are tried.

The \gls{FRF} is estimated using the local modeling approaches indicated in \tabref{tbl:nparam:methods}.

@@

We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=2000$ Monte Carlo runs of the simulations above.
Specifically, the following values
\begin{align}
  \sampleMean{\bullet}(\omega_k) & 
  \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k)
  \\
  \sampleBias{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
    = 
    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
    \\
    \sampleVariance{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC - 1}
    \sum_{i=1}^{\nMC}
                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
\end{align}
are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$.

  % \subsection{Implications of the model structure}
  % \subsection{Implications of the noise level}
  % \subsection{Implications of the noise coloring}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
  \label{}
\end{figure}

As the Monte Carlo simulations yield the estimated \gls{FRF}, the bias and variance for the different methods as a function of frequency, a huge amount of data is generated.
To interpret the data, we aggregate the observed values over the frequencies to obtain:
\begin{align}
  \sampleVariance{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleVariance{\bullet}(\omega_k)} \\
  \sampleBias{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleBias{\bullet}(\omega_k)}
\end{align}
which can be visualized for the different values of the $\SNR$, $\nBW$ and for each method.

@@

For the more noisy situation where $\SNR = 40 \unit{dB}$ (\figref{fig:nparam:comparison:midSNR}), the situation is qualitatively equal except the bias incurred by the \gls{LRM} is similar to the noise level.

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
  \label{fig:nparam:comparison:SNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
  \label{fig:nparam:comparison:midSNR}
\end{figure}

@@

### 2016-04-24 ch03-lrm/nonparametric.tex
Many TODOs in ch03

  \section{Conclusion}
  \label{sec:conclusion}

  \begin{itemize}
    \item LRM: extension to LRIC
    \item LRM: derivation of bias
    \item LRM vs LPM: at which settings is LRM better than LPM
    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
  \end{itemize}

>>>>

  \section{Conclusion}
  \label{sec:conclusion}
In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
Since the \gls{LRM} is an inherently biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
Hence, expressions for the bias of the \gls{LRM} were derived.
For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LRM}.
For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
For
In this chapter, the \gls{LRIC} was introduced.
This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.

Relatedly, two approaches to aid in performing the bias-variance trade-off for these local methods are illustrated.
First, a short study of cross-validation for local models is given.
Secondly, an approach to truncate the impulse response obtained from the \gls{LPM} is illustrated.
The latter can improve the performance of the \gls{LPM} considerably if a large number of noisy samples is measured.
